maze-dataset: Maze Generation with Algorithmic Variety and Representational Flexibility

### 2025-04-09 docs/paper/paper.tex
fix docs link
fix page breaks

\begin{table}[H]
\centering
\begin{tabular}{|ll|r|rrr|}
  \hline
  maze\_ctor
          & keyword args           & all sizes 
                                              & \shortstack{small \\ $g \leq 10$} 
                                                         & \shortstack{medium \\ $g \in (10, 32]$} 
                                                                    & \shortstack{large \\ $g > 32$} \\
  \hline\hline
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_dfs}{dfs}
          &                        &   28.0   &    2.8   &   20.3   &  131.8   \\
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_dfs}{dfs}
          & accessible\_cells=20   &    2.3   &    2.2   &    2.4   &    2.2   \\
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_dfs}{dfs}
          & do\_forks=False        &    2.7   &    2.2   &    3.1   &    3.5   \\
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_dfs}{dfs}
          & max\_tree\_depth=0.5   &    2.5   &    2.0   &    2.7   &    4.0   \\
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_dfs_percolation}{dfs\_percolation}
          & p=0.1                  &   43.9   &    2.8   &   33.9   &  208.0   \\
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_dfs_percolation}{dfs\_percolation}
          & p=0.4                  &   48.7   &    3.0   &   36.5   &  233.5   \\
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_kruskal}{kruskal}
          &                        &   12.8   &    1.9   &   10.3   &   55.8   \\
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_percolation}{percolation}
          & p=1.0                  &   50.2   &    2.6   &   37.2   &  242.5   \\
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_recursive_division}{recursive\_div}
          &                        &   10.2   &    1.7   &    8.9   &   42.1   \\
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_wilson}{wilson}
          &                        &  676.5   &    7.8   &  188.6   & 3992.6   \\
  \hline\hline
  mean
          &                        &  559.9   &   13.0   &  223.5   & 3146.9   \\
  median
          &                        &   11.1   &    6.5   &   32.9   &  302.7   \\
  \hline
\end{tabular}
\caption{Generation times for various algorithms and maze sizes. More information can be found on the \docsref{benchmarks}{benchmarks page}.}
\label{tab:benchmarks}
\end{table}

\begin{figure}
\hypertarget{fig:benchmarks}{%
\centering
\includegraphics[width=0.95\textwidth,height=\textheight]{figures/benchmarks/gridsize-vs-gentime.pdf}
\caption{Plot of maze generation time. Generation time scales
exponentially with maze size for all algorithms. Generation time per
maze does not depend on the number of mazes being generated, and there
is minimal overhead to initializing the generation process for a small
dataset. Wilson's algorithm is notably less efficient than others and
has high variance. Note that values are averaged across all parameter
sets for that algorithm. More information can be found on the
\href{https://understanding-search.github.io/maze-dataset/benchmarks/}{benchmarks
page}.}\label{fig:benchmarks}
}
\end{figure}

>>>>

\begin{table}[H]
\centering
\begin{tabular}{|ll|r|rrr|}
  \hline
  maze\_ctor
          & keyword args           & all sizes 
                                              & \shortstack{small \\ $g \leq 10$} 
                                                         & \shortstack{medium \\ $g \in (10, 32]$} 
                                                                    & \shortstack{large \\ $g > 32$} \\
  \hline\hline
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_dfs}{dfs}
          &                        &   28.0   &    2.8   &   20.3   &  131.8   \\
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_dfs}{dfs}
          & accessible\_cells=20   &    2.3   &    2.2   &    2.4   &    2.2   \\
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_dfs}{dfs}
          & do\_forks=False        &    2.7   &    2.2   &    3.1   &    3.5   \\
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_dfs}{dfs}
          & max\_tree\_depth=0.5   &    2.5   &    2.0   &    2.7   &    4.0   \\
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_dfs_percolation}{dfs\_percolation}
          & p=0.1                  &   43.9   &    2.8   &   33.9   &  208.0   \\
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_dfs_percolation}{dfs\_percolation}
          & p=0.4                  &   48.7   &    3.0   &   36.5   &  233.5   \\
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_kruskal}{kruskal}
          &                        &   12.8   &    1.9   &   10.3   &   55.8   \\
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_percolation}{percolation}
          & p=1.0                  &   50.2   &    2.6   &   37.2   &  242.5   \\
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_recursive_division}{recursive\_div}
          &                        &   10.2   &    1.7   &    8.9   &   42.1   \\
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators.gen_wilson}{wilson}
          &                        &  676.5   &    7.8   &  188.6   & 3992.6   \\
  \hline\hline
  mean
          &                        &  559.9   &   13.0   &  223.5   & 3146.9   \\
  median
          &                        &   11.1   &    6.5   &   32.9   &  302.7   \\
  \hline
\end{tabular}
\caption{Generation times for various algorithms and maze sizes. More information can be found on the \href{https://understanding-search.github.io/maze-dataset/benchmarks}{benchmarks page}.}
\label{tab:benchmarks}
\end{table}

\begin{figure}
\hypertarget{fig:benchmarks}{%
\centering
\includegraphics[width=0.9\textwidth,height=\textheight]{figures/benchmarks/gridsize-vs-gentime.pdf}
\caption{Plot of maze generation time. Generation time scales
exponentially with maze size for all algorithms. Generation time per
maze does not depend on the number of mazes being generated, and there
is minimal overhead to initializing the generation process for a small
dataset. Wilson's algorithm is notably less efficient than others and
has high variance. Note that values are averaged across all parameter
sets for that algorithm. More information can be found on the
\href{https://understanding-search.github.io/maze-dataset/benchmarks/}{benchmarks
page}.}\label{fig:benchmarks}
}
\end{figure}
